### 2017-05-22 sections/introduction.tex
Update on Overleaf.

The quality of any compression method depends on the nature of input data. Therefore, several different non-trivial finite element analyses are used as benchmarks for an implementation of the compression algorithm. The ability to control the quality of compression results is the key requirement for an implementation.

>>>>

Compression methods usually yield approximated data. In the following text, the term \textit{approximation error} denotes an error resulted from compression, i.e. difference between original results of FEM analysis and their compressed form. It should not be confused with the error of the Finite element method that yields approximate solution to mathematical problems used to model physical reality.

The quality of any compression method depends on the nature of input data. Therefore, several different non-trivial finite element analyses are used as benchmarks for an implementation of the compression algorithm. The ability to control the quality of compression is the key requirement for an implementation of the compression algorithm.
